\documentclass{article}
\usepackage{graphicx}
\usepackage{todonotes}

\begin{document}
\title{Measuring Sexually Explicit Content Online Ethics Approval}
\author{Christopher Forbes}

\maketitle

\begin{abstract}
To investigate the means of measuring sexually explicit material in documents.
\end{abstract}

\section*{Hypothesis}
I aim to prove that my software will rank these documents in the order of

'1,2,3,4,5,6,7,8,9,10'
\section*{Experiment Participants}
Ideally i would like between six and eight participants aged 20+ (due to the material requiring analysis see test data).
\section*{Procedure}
\begin{description}
\item[introduction]
When the participants arrive, i will introduce myself and the title of my project.
\item[ethics]
After the introduction i will explain to them the aim of the experiment, and explain if at any point they feel uncomfortable with the text provided they may stop the experiment and leave no questions asked.
\item[Data protection]
No personal data will be gathered during this experiment, I will purely be gathering information on the order of the documents.
\item[Before we begin]
I will give each participant the opportunity to ask me any questions before the experiment begins
\item[During the experiment]
During the experiment i will leave them for approxamately 10 mins, or until they have completed the experiment. I will only be concerned with the final ordering of the documents.
\item[Analysis]
Once each participant has completed the task, i will make a note of the positions that each of the ten documents is in, and calculate the average position of each document.
\end{description}
\section*{Variables}
When asking for participants from the computer science faculty i must be aware that many students from the CIS departments spend much of their time online, as such may have built up a mental tolerance to particular words or phrasings. Subsequtnely skewing the results to the lower end of the spectrum. In an attempt to avoid this from happening i will ideally be able to get participants from some of the other years (not only fourth year).

\section*{Parameters}
Each participant will be given ten paragraphs of text (each approxamatley eight to ten lines of text) asked to read each paragraph then place each of the paragraphs into order ranging from the least explicit text to the most explicit.

\section*{Intended use for data}
I intend to use the data gathered from the experiments to order each of the ten documents, based on the average position it is placed in by the participants. I then intend to run each of these documents through my software and work out the order which it places them based on the keyword density assigned to each document.

Finally I will compare the positions calculated by the keyword density algorithm and compare them to the positions they are placed in by the participants.

\section*{Test Data 1}
\todo{I'm not sure whether to use the full words or whether to try and censor it a bit also im not sure whether censoring would reduce the explicitness to the user. Thus skewing the data gathered.}
\todo{This is an exert from the wikipedia page for genitals it is eductional but still explicit}
The visible portion of the human genitals for males consists of scrotum and a penis, for females it consists of the labia, clitoris and vagina. Women have two genital orifices, the vagina and urethra, while men have only one, the urethra. Both male and female genitals have many nerve endings, resulting in pleasurable and highly sensitive touch.
In most civilized human societies, particularly in conservative ones, genitals are considered a public indecency and sometimes even illegal if left uncovered in public.
\\
\\
\\
\section*{Test Data 2}
The pussy cat licked his paw and rubbed his ears. Then he relaxed exposed only to the warmth of the sunlight and the comfort of the shag carpet.
When his owner came she scratched behind his ear with her finger. 
To finish his day off the pussy cat tried to play with the sprinkler in the garden but got squirted in the face.
\todo{I have written this one rather carefully as it has several keywords in it whilst it is in no way offensive or explicit}
\section*{Test Data 3}
Dave: hey dude
\newline
John: Howsit
\newline
Dave: not bad, i got slapped in the balls today
\newline
John: must have been a good shot
\newline
Dave: I have big balls 
\newline
John: Sure you do... :P
\newline
Dave: fuck you :P
\todo{This is a very generic chat between two guys, nothing in particularly explicit in here just a generic chat}
\section*{Test Data 4}
JoXXS: yo bbz
\newline
AMEE:hey bbz uu2?
\newline
joXXS:nm u cummin ovr 2nite?
\newline
AMEE: duno yet
\newline
joXXS:omg you have to cumm
\newline
AMEE: my dad wnt bring me, so its hard to get there
\newline
joXXS:gt a taxi and bang your here easi :)
\section*{Test Data 5}
\todo{So far the test data has been relativly benign with nothing really explicit however i feel my software would class them as explicit as it currently stands. Here i am thinking of taking exerts from the chatlogs before now i have been making them up as i go along}
Y [12:48 PM]: ur profi says ur a boy scot dude they not rich 
\newline
X [12:48 PM]: yeah but i have plenty from an inheritance boi 
\newline
Y [12:49 PM]: u really a boy scot? 
\newline
Y [12:50 PM]: ? 
\newline
X [12:50 PM]: yes, of course i am 
\newline
Y [12:50 PM]: thats so gay 
\newline
X [12:51 PM]: why, you should see some of those bois naked bodies, waht a turn on ,,its hard to not want them 
\\
\\
\\
\section*{Test Data 6}
\todo{a modified chatlog}
Gary:Hey slut
\newline
Mark:Hey!
\newline
Mark:ya prick
\newline
Mark:How the fuck you doing shit face?
\newline
Gary:not bad yah mad cunt
\newline
Gary:hows shit?
\newline
Mark:Shits fan fucking tastic! Some bastard farted on the train. Mad dick.
\newline
Gary:that sounds fantastic
\newline
Gary:i have been learning some form of archaic wizardry all fucking morning
\section*{Test Data 7}
\todo{modified chatlog}
692005 (7:13:48 PM): so are you a thong kind of girl? 
\newline
erin78 (7:14:00 PM): no not really
\newline
692005 (7:14:15 PM): that sucks..bet you would look awesome in one
\newline
692005 (7:14:21 PM): so what are you wearing now?
\newline
erin78 (7:14:32 PM): jeans n a tshirt
\newline
692005 (7:14:41 PM): nice..do you have a cam?
\newline
erin78 (7:15:09 PM): no
\newline
692005 (7:15:32 PM): I am thinking...I bet you have some nice pink nipples
\newline
erin78 (7:15:43 PM): u wrong 

\section*{Test Data 8}
olfe (1:50:12 PM): Oh? NP... But, if I did this, it would have to be done in secret and you would have to be totally submissive.
\\
olfe (1:50:14 PM): Yes, you would.
\\
grrl (1:50:37 PM): as long as you keep me safe ill do whatever you say. 
\\
olfe (1:50:42 PM): Good...
\\
olfe (1:50:48 PM): Now, are you sure you want to do this?
\\
grrl (1:51:01 PM): yes
\\
olfe (1:51:13 PM): 100%?
\\
grrl (1:51:32 PM): if youll keep me safe, yes
\\
olfe (1:51:33 PM): Knowing that you cannot change your mind, if you do. 
\\
olfe (1:51:35 PM): I will. 
\\
\\
\\
\section*{Test Data 9}
X: Hey sexy
\\
y: Aw'ryt hot stuff
\\
y: did you have fun last night?
\\
X: you know i did big boi
\\
y: thought so ;)
\\
X: what you doing just now
\\
y: ;) wouldn't you like to know...

\section*{Test Data 10}
kalo (12:02:56 AM): girls who know they should submit
\\
keri (12:03:12 AM): o lol
\\
keri (12:03:23 AM): thats wat he said i am
\\
keri (12:03:29 AM): submissive lol
\\
keri (12:03:44 AM): that wat u mean?
\\
kalo (12:03:52 AM): yeah
\\
kalo (12:04:36 AM): I mean, you'd wear something if I asked you to wouldn't you?
\\
keri (12:05:32 AM): yea
\\
kalo (12:05:57 AM): how short do your skirts get?

\end{document}
